The Birth of a Galaxy: Population III Metal Enrichment and Population II Stellar Populations

### 2010-10-14 ms.tex
Made corrections to the first draft after read-thru.

  Population III stars first form in dark matter halos with masses
  around $10^6 \Ms$.  By definition, they are metal-free, and their
  protostellar collapse is driven by molecular hydrogen cooling in the
  gas-phase, leading to a massive characteristic mass $\sim 100~\Ms$
  and suppressed fragmentation.  Population II stars with lower
  characteristic masses form when the star-forming gas reaches a
  critical metallicity of $10^{-6} - 10^{-3}~Z_\odot$, depending on
  whether dust cooling is important.  We present adaptive mesh
  refinement radiation hydrodynamics simulations that
  self-consistently follow the transition from Population III to II
  star formation.  We model stellar radiative feedback with adaptive
  ray tracing.  A top-heavy initial mass function for the Population
  III stars is considered, resulting in a plausible distribution of
  pair-instability supernovae and associated metal enrichment.  We
  find that the gas fraction recovers from 5 percent to nearly the
  cosmic fraction in halos with merger histories rich in halos above
  $10^7 \Ms$.  A single pair-instability supernova is sufficient to
  enrich the host halo to a metallicity floor of $10^{-3} Z_\odot$ and
  to transition to Population II star formation.  Neighboring halos
  are enriched to metallicities 10--100 times lower as the enriching
  blastwaves mainly bypass them.  Stellar metallicities trace gas
  metallicities within 0.2 dex.  We find that stellar metallicities do
  not necessarily trace stellar ages, as mergers of halos with
  established stellar populations can create superpositions of $t-Z$
  evolutionary tracks.  We see a bimodal metallicity distribution that
  is created after a starburst occurs when the halo can cool
  efficiently through atomic line cooling.

@@

The transition from Pop III to Pop II star formation is solely
dependent on the propagation of metals from the SNe remnants into
future sites of star formation.  Their flows are complex because of
the interactions between the SN blastwave, cosmological accretion and
halo mergers, and nearby stellar feedback.  In minihalos ($M_{\rm h}
\sim 10^6~\Ms$), radiation from the massive Pop III drives a 30
\kms~shock, which is 10 times greater than the escape velocity of the
halo, and leaves behind a warm ($3 \times 10^4$ K) and diffuse (0.5
\cubecm) medium \citep{Kitayama04, Whalen04, Abel07}.  The latter
feature aids in the expansion of the blastwave because it delays the
transition to the Sedov-Taylor and snowplow phases.  In PISNe,
approximately half of the metals stay in the IGM with an metal bubble
size of a few kpc.  The remaining metals fall back into the host halo.
The blastwave may induce star formation in nearby halos through the
compression of the gas \citep{Ferrara98}; however timescales for metal
mixing into the dense gas are many dynamical times \citep{Cen08} for
shock velocities $\lsim 100~\kms$.

Numerical simulations are useful to detangle and study these
complexities and the transition from Pop III to II stars.  In this
Letter, we present the simulations that include both types of star
formation, its radiative feedback, and its SNe feedback.  We utilize
an initial mass function (IMF) for individual Pop III stars, based on
the latest simulation results.  The methods used here incorporate and
link together recent results from metal-enriched and metal-free star
formation, the critical metallicity, and pair-instability supernovae.
Furthermore we spatially distinguish metal enrichment from Pop II and
Pop III stars.  This is the first time that all of these processes
have been interconnected in a simulation that resolves minihalos to
study the transition to Pop II star formation self-consistently.  We
describe our simulation setup and our adopted star formation models in
\S \ref{sec:setup} and present our results in \S \ref{sec:results}.
We discuss the implications of our findings and conclude in the last
section.

@@

In this section, we first describe our simulation setup.  We then
detail the star formation models used in these simulations and how we
model stellar radiation and SNe feedback.

@@

We use the adaptive mesh refinement (AMR) code
\enzo~\citep{BryanNorman1997, OShea2004} that employs our
implementation of adaptive ray tracing for radiation transport
\citep{Wise10}.  We have modified \enzo~to use the HLLC Riemann solver
\citep{Toro94_HLLC} for additional stability in strong shocks.  To
resolve minihalos with at least 100 dark matter (DM) particles and
follow the formation of the first generation of dwarf galaxies, we use
a simulation box of 1 Mpc that has a resolution of $256^3$.  This
gives us a DM mass resolution of 1840 \Ms.  We refine the grid on
baryon overdensities of $3 \times 2^{-0.2l}$, where $l$ is the AMR
level, resulting in a super-Lagrangian behavior.  We also refine on a
DM overdensity of $3 \times 2^l$ and always resolve the local Jeans
length by at least 4 cells.  The latter criterion avoids any
artificial fragmentation during gaseous collapses \citep{Truelove97}.
We initialize the simulation with \textsl{grafic}
\citep{Bertschinger01} at $z = 130$ and use the cosmological
parameters from the 7-year WMAP data \citep{WMAP7}: $\Omega_M =
0.266$, $\Omega_\Lambda = 0.734$, $\Omega_b = 0.0449$, $h = 0.71$,
$\sigma_8 = 0.81$, and $n = 0.963$ with the variables having their
usual definitions.  The size of the box limits the simulation to an
ending point of $z=7$.

We use a non-equilibrium chemistry solver with 9 species of hydrogen,
helium, and molecular hydrogen \citep{Abel97}.  We will follow-up this
study with one that considers radiative cooling from metal-enriched
gas, using rates that are calculated from CLOUDY \citep{CLOUDY} and
the method of \citet{2008MNRAS.385.1443S}.

@@

We distinguish Pop II and Pop III star formation by the metallicity of
the densest cell in the molecular cloud.  Pop II stars are formed if
[Z/H] $> -4$, and Pop III stars are formed otherwise.  We do not
consider Pop III.2 stars and intermediate mass stars from CMB-limited
cooling.

@@

For Pop III stars, we use the same star formation model as
\citet{Abel07} and \citet{Wise08_Gal} where each star particle
represents a single star.  The critical overdensity in which a star
forms is $5 \times 10^5$.  Instead of using a fixed stellar mass, we
randomly sampled from an IMF with a functional form of
%
\begin{equation}
\label{eqn:imf}
f(M)dM = M^{-1.3} \exp\left[-\left(\frac{M_{\rm char}}{M}\right)^{1.6}\right]
\end{equation}
to determine the stellar mass.  Above $M_{\rm char}$, it behaves as a
Salpeter IMF but is exponentially cutoff below that mass
\citep{Chabrier03, Clark09}.  For reproducibility, we record the
number of times the random number generator \citep[Mersenne
  twister;][]{MTwister} has been called for use when restarting the
simulations.

@@

We treat Pop II star formation with the same prescription as
\citet{Wise09}, which is a modified version of the widely used
\citet{Cen92} method but accounts for the fact that the molecular
clouds are resolved.  The critical overdensity is the same as the Pop
III star formation model.  In each star-forming region, a fraction
$c_* = 0.07$ of the cold gas ($T < 10^3$ K) is removed from the grid
and deposited into the star particle.  Each star particle lives for 20
Myr, the maximum lifetime of an OB star.  These stars generate the
majority of the ionizing radiation and SNe feedback in stellar
clusters, thus we ignore lower mass stars.  We discuss our treatment
of stellar feedback next.

@@

The Pop II stars emit 6000 hydrogen ionizing photons per baryon over
their lifetime, and we do not consider singly- and doubly-ionizing
helium photons.  We note that low-metallicity stars generate up to a
factor of four more ionizing photons than a solar metallicity
population \citep{Schaerer03} and might be underestimating the
radiative feedback.  Nonetheless this study provides an excellent
first insight in the transition to Pop II star formation, as the metal
enrichment is the key ingredient here.  For SN feedback, these stars
generate $6.8 \times 10^{48}$ erg s$^{-1}$ $\Ms^{-1}$ of energy after
living for 4 Myr, which is injected into spheres with a radius of 10
pc.  If the resolution of the grid is less than 10/3 pc, we deposit
the energy into a $3^3$ cube surrounding the star particle.

@@

\begin{figure*}
  \epsscale{0.8}
  \plotone{f3}
  \epsscale{1}
  \caption{\label{fig:projections} Density-weighted projections of gas
    density (top), temperature (middle), and metallicity (bottom) at
    $z=7$.  The left column shows the entire simulation volume, where
    the center and right columns focus on the intense and quiet halos,
    respectively.  The metallicity projections are a composite picture
    of metals originating from Pop III (red) and Pop II (blue) stars.}
\end{figure*}

Here we present the gaseous and stellar evolution of two selected
halos in the simulation: one that has an early mass buildup but no
major mergers after $z=12$, and one that experiences a series of major
mergers between $z=10$ and $z=7$.  We name the halos ``quiet'' and
``intense'', respectively.  We start with the birth of the first Pop
III star in its merger history.  We then compare the nature of star
formation in these halos.

@@

Figure \ref{fig:evo} shows the total, metal-enriched stellar, and gas
mass history of the most massive progenitors of both halos.  The quiet
halo undergoes a series of major mergers at $z > 12$, growing by a
factor of 30 to $2.5 \times 10^7 \Ms$ within 150 Myr.  Afterwards it
only grows by a factor of 3 by $z=7$ mainly through smooth accretion
from the filaments and IGM.  It is the most massive halo in the
simulation between redshifts 13 and 10.  At the same time, the intense
halo has a relatively small mass $M = 10^7 \Ms$, but it is contained
in a biased region on a comoving scale of 50 kpc with $\sim30$ halos
with $M > 10^6 \Ms$.  After $z=10$, these halos hierarchically merge
to form a $10^9 \Ms$ halo at $z=7$ with two major mergers at redshifts
10 and 7.9, seen in the rapid increases in total mass in Figure
\ref{fig:evo}.  The merger history of the two halos are not atypical
as dark matter halos can experience both quiescent and vigorous mass
accretion rates in their buildup.

Both halos star forming Pop II stars when $M = 10^7 \Ms$.  This is
consistent with the filtering mass $M_f$ of high-redshift halos when
it accretes mainly from a pre-heated IGM \citep{gnedin98, gnedin00,
  Wise08_Gal}.  Afterwards these halos can cool efficiently through
molecular and atomic hydrogen cooling, sustaining constant and
sometimes bursty star formation.  The latter characteristic is equated
with the definition of a galaxy.  The quiet halo forms $10^5 \Ms$ of
stars by $z=9$.  This initial starburst photo-evaporates the majority
of its molecular clouds, in addition to heating and ionizing the
surrounding IGM out to a radius of 10--15 kpc at $z=9$.  These
respectively reduce the in-situ and external cold gas supply that
could feed future star formation.

The gas fractions of both halos are depleted from 0.15 to 0.08 by
outflowing shocks driven by ionization fronts in their initial
starbursts.  The quiet halo never recovers to the cosmic fraction
$\Omega_b/\Omega_M$ for the following reason.  The lack of major
mergers of halos above the filtering mass leads to a small gas
fraction, cold gas reservoir, and stellar mass at later times.  This
plays a large role in gas accretion because halos with $M < M_f$ will
be likely photo-evaporated, hosting diffuse warm gas reservoirs
instead of cold dense cores.  During this quiescent period, the halo
mainly accretes warm diffuse gas from the filaments and IGM.  In
contrast, the intense halo grows from major mergers of halos with $M >
M_f$.  The progenitor halos involved in the major mergers are able to
host molecular clouds and have, in general, higher gas fractions.
Between $z=10$ and $z=8$, the gas fraction increases from 0.07 to 0.12
until it rapidly jumps to 0.14 when a gas-rich major merger occurs.
The stellar mass accordingly increases with the ample supply of cold
gas during this period.  The gas fraction then decreases slightly by
0.01 when galactic outflows are generated from the starburst
associated with this major merger.

@@

The evolution of the stellar and gas metallicity of both halos are
illustrated in Figure \ref{fig:Zevo}.  PISNe from Pop III stars enrich
the nearby IGM out to a radius of 10 kpc and provides a metallicity
floor of $[Z_3/H] \sim -3$ in both halos, given $M_{\rm char} = 100
\Ms$.  The metallicity from Pop II SNe initially enrich the ISM of
both halos to an average $[\bar{Z}_2/H]$ between --3.5 and --3.  The
quiet halo is enriched to $[\bar{Z}_2/H] \sim -2.5$ until the
metal-poor inflows balance the metal-rich galactic outflows, which are
directed in the polar directions of the gas disk.  This is apparent in
the metallicity projections in Figure \ref{fig:projections}.  The
average stellar metallicities is equal or slightly higher up to 0.5
dex than $[\bar{Z}_2/H]$.

At $z \sim 8$, the metallicity of the intense halo dramatically
self-enriches itself by a factor of 30 to $[\bar{Z}_2/H] = -1.5$
during a starburst.  Because this halo is located in a large-scale
overdensity, the ejecta falls back into the halo after reaching
distances up to 20 comoving kpc, in turn keeping the halo gas
metallicity high because the inflows are relatively metal-rich
themselves.  The first few Pop II star clusters have [Z/H] between --1
and --2 and dominate the average stellar metallicity at $z > 8$.
After the $z \sim 8$ starburst, the average stellar metallicity
follows the average gas metallicity within 0.1 dex.

@@

\textit{Quiet halo}.--- The most massive progenitor interestingly
never hosts a Pop III star.  Instead a nearby halo forms a Pop III
star, which (randomly) produces a PISNe at $z=16$.  The blastwave
overruns the most massive progenitor, and the dense core survives this
event and is enriched by this PISN, triggering the transition to Pop
II star formation.  Other progenitors host three Pop III stars,
forming at $z = 15.4, 14.2, 13.8$, with the latter producing a PISN.
Metal enrichment from these two PISNe and Pop II SF quench Pop III
star formation in this halo.

\textit{Intense halo}.--- The progenitors host a total of 56 Pop III
stars with 21 producing PISNe.  The first forms in a $6 \times 10^5
\Ms$ halo at $z=19$.  Pop III stars form on a regular interval in the
halo's progenitors until $z=9$ when most of these halos enter the
metal-rich bubble surrounding the intense halo.  There are two Pop III
stars forming at $z=7.7$ with [Z/H] = --5.7, whose molecular clouds
were enriched by external blastwaves that only partially enriched the
dense regions \citep{Cen08}.  The most massive progenitors of the
intense halo cease to form Pop III stars at $z<12$ because of nearby
or intrinsic PISNe.

@@

\begin{figure*}
  \plottwo{f4a}{f4b}
  \caption{\label{fig:pops} The scatter plots show the star formation
    history of the quiet (left) and intense (right) halos as a
    function of metallicity at $z=7$.  Each circle represents a star
    cluster, whose area is proportional to its mass.  The open circles
    in the upper right represent sizes of $10^3$, $10^4$, and $10^5$
    \Ms~star clusters.  The dashed lines in the right panel guide the
    eye to two stellar populations that were formed in two satellite
    halos, merging at $z=7.5$.  The upper histogram collects the star
    formation history into 25 equal temporal bins.  The right
    histogram depicts the stellar metallicity distribution.}
\end{figure*}

@@

Figure \ref{fig:pops} shows the star formation history of both halos.
From this plot, the metallicity distribution, star formation rates,
and metallicity evolution and spread at a given time can all be
extracted from these data.

\textit{Quiet halo}.--- A nearby PISNe provides a metallicity floor of
[Z/H] = --2.8 at which metallicity the first Pop II stars form.  The
stellar metallicity evolution exhibits what is expected from a
relatively isolated system with the stellar feedback steadily
enriching the ISM, resulting in a correlation between stellar age and
metallicity.  After $z=10$ the metallicities plateau at [Z/H] = --2.1
for reasons discussed in \S\ref{sec:halo}.  The SFR peaks at $z=10$
and decreases as the cold gas reservoir is depleted.  Around $z=7.5$,
a 25:1 minor merger occurs, and the gas inside the satellite halo is
compressed, triggering metal-poor, [Z/H] = --3.2, SF during its
nearest approach.  This halo infalls through a filament, where most of
metal enrichment in the quiet halo occurs in bi-polar flows
perpendicular to the galaxy disk and filament.  The filament and thus
this satellite halo remains relatively metal-poor.  The bi-polar
outflows and metal-poor filaments are seen in the metallicity
projections in Figure \ref{fig:projections}.  Stars with [Z/H] $<$ --3
compose 1.6 percent of the total stellar mass.

\textit{Intense halo}.--- In contrast with the quiet halo, the intense
halo undergoes a few major mergers of halos with an established
stellar population.  This creates a superposition of age-metallicity
tracks in the SFH, seen in the complexity of Figure \ref{fig:pops}.
The first two Pop II stellar clusters have an unusually high
metallicity [Z/H] $\sim$ --1, which occurs when a PISN blastwave
trigger star formation in two neighboring halos.  Most of the early
star formation occurs around [Z/H] = --2.5.  At $z=9$, the halo's
virial temperature reaches \tento{4} K.  This combined with a 10:1
merger creates a starburst that quickly enriches the halo to [Z/H] =
--1.5 by $z=8$.  The halo continues to enrich itself with further SF
until $z=7$.  The spikes in the scatter plot correspond to SN
triggered star formation in nearby molecular clouds that are enriched
up to a factor of 10 with respect to the ISM.  However the mass
fraction of these metal-rich, SN triggered clusters are small compared
to the total stellar mass.  The starburst at $z=9$ creates a bimodal
metallicity distribution with peaks at [Z/H] = --2.4 and --1.2 with
the metal-rich component mainly being created after the starburst.
Two systems with sizable stellar components merge into the halo at $z
\sim 8$, and their stellar populations are still discernible in the
metallicity-age plot, whose tracks are noted by dashed lines.  Stars
with [Z/H] $<$ --3 compose 1.8 percent of the total stellar mass.

>>>>

  Population III stars first form in dark matter halos with masses
  around $10^6 \Ms$.  By definition, they are metal-free, and their
  protostellar collapse is driven by molecular hydrogen cooling in the
  gas-phase, leading to a massive characteristic mass $\sim 100~\Ms$
  and suppressed fragmentation.  Population II stars with lower
  characteristic masses form when the star-forming gas reaches a
  critical metallicity of $10^{-6} - 10^{-3}~Z_\odot$, depending on
  whether dust cooling is important.  We present adaptive mesh
  refinement radiation hydrodynamics simulations that follows the
  transition from Population III to II star formation.  We model
  stellar radiative feedback with adaptive ray tracing.  A top-heavy
  initial mass function for the Population III stars is considered,
  resulting in a plausible distribution of pair-instability supernovae
  and associated metal enrichment.  We find that the gas fraction
  recovers from 5 percent to nearly the cosmic fraction in halos with
  merger histories rich in halos above $10^7 \Ms$.  A single
  pair-instability supernova is sufficient to enrich the host halo to
  a metallicity floor of $10^{-3} Z_\odot$ and to transition to
  Population II star formation.  Neighboring halos are enriched to
  metallicities 10--100 times lower as the enriching blastwaves mainly
  bypass them.  Stellar metallicities trace gas metallicities within
  0.2 dex.  We find that stellar metallicities do not necessarily
  trace stellar ages, as mergers of halos with established stellar
  populations can create superpositions of $t-Z$ evolutionary tracks.
  A bimodal metallicity distribution is created after a starburst
  occurs when the halo can cool efficiently through atomic line
  cooling.

@@

The transition from Pop III to Pop II star formation (SF) is solely
dependent on the propagation of metals from the SNe remnants into
future sites of SF.  Their flows are complex because of the
interactions between the SN blastwave, cosmological accretion and halo
mergers, and nearby stellar feedback.  In minihalos ($M_{\rm h} \sim
10^6~\Ms$), radiation from the massive Pop III drives a 30 \kms~shock,
which is 10 times greater than the escape velocity of the halo, and
leaves behind a warm ($3 \times 10^4$ K) and diffuse (0.5 \cubecm)
medium \citep{Kitayama04, Whalen04, Abel07}.  This aids in the
expansion of the blastwave because it delays the transition to the
Sedov-Taylor and snowplow phases.  In PISNe, approximately half of the
metals stay in the IGM with an metal bubble size of a few kpc.  The
remaining metals fall back into the host halo.  The blastwave may
induce SF in nearby halos through the compression of the gas
\citep{Ferrara98}; however timescales for metal mixing into the dense
gas are many dynamical times \citep{Cen08} for shock velocities $\lsim
100~\kms$.

Numerical simulations are useful to detangle and study these
complexities and the transition from Pop III to II stars.  In this
Letter, we present the simulations that include both types of SF, and
their radiative and mechanical feedback.  We utilize an initial mass
function (IMF) for individual Pop III stars, based on the latest
simulation results.  The methods used here incorporate and link
together recent results from metal-enriched and metal-free star
formation, the critical metallicity, and pair-instability supernovae.
Furthermore we spatially distinguish metal enrichment from Pop II and
Pop III stars.  This is the first time that all of these processes
have been interconnected in a simulation that resolves star-forming
minihalos to study the transition to Pop II star formation.  We
describe our simulation setup and our adopted SF models in \S
\ref{sec:setup} and present our results in \S \ref{sec:results}.  We
discuss the implications of our findings and conclude in the last
section.

@@

In this section, we first describe our simulation setup.  We then
detail the SF models used here and how we model radiative and SNe
feedback.

@@

We use the adaptive mesh refinement (AMR) code
\enzo~v2.0\footnote[\dag]{\texttt{lca.ucsd.edu/enzo, unstable
    changeset b86d8ba026d6}} \citep{BryanNorman1997, OShea2004}, which
has been modified to use a HLLC Riemann solver \citep{Toro94_HLLC} for
additional stability in strong shocks.  To resolve minihalos with at
least 100 dark matter (DM) particles and follow the formation of the
first generation of dwarf galaxies, we use a simulation box of 1 Mpc
that has a resolution of $256^3$.  This gives us a DM mass resolution
of 1840 \Ms.  We refine the grid on baryon overdensities of $3 \times
2^{-0.2l}$, where $l$ is the AMR level, resulting in a
super-Lagrangian behavior.  We also refine on a DM overdensity of $3
\times 2^l$ and always resolve the local Jeans length by at least 4
cells, avoiding artificial fragmentation during gaseous collapses
\citep{Truelove97}.  We initialize the simulation with \textsl{grafic}
\citep{Bertschinger01} at $z = 130$ and use the cosmological
parameters from the 7-year WMAP data \citep{WMAP7}: $\Omega_M =
0.266$, $\Omega_\Lambda = 0.734$, $\Omega_b = 0.0449$, $h = 0.71$,
$\sigma_8 = 0.81$, and $n = 0.963$ with the variables having their
usual definitions.  We stop the simulation at $z=7$.

We use a non-equilibrium chemistry solver with 9 species of hydrogen,
helium, and molecular hydrogen \citep{Abel97}.  We will follow-up this
study with one that considers radiative cooling from metal-enriched
gas, using the method of \citet{2008MNRAS.385.1443S}.

@@

We distinguish Pop II and Pop III SF by the metallicity of the densest
cell in the molecular cloud.  Pop II stars are formed if [Z/H] $> -4$,
and Pop III stars are formed otherwise.  We do not consider Pop III.2
stars and intermediate mass stars from CMB-limited cooling.

@@

For Pop III stars, we use the same SF model as \citet{Abel07} and
\citet{Wise08_Gal} where each star particle represents a single star.
The critical overdensity in which a star forms is $5 \times 10^5$.
Instead of using a fixed stellar mass, we randomly sampled from an IMF
with a functional form of
%
\begin{equation}
\label{eqn:imf}
f(M)dM = M^{-1.3} \exp\left[-\left(\frac{M_{\rm char}}{M}\right)^{1.6}\right]
\end{equation}
to determine the stellar mass.  Above $M_{\rm char}$, it behaves as a
Salpeter IMF but is exponentially cutoff below that mass
\citep{Chabrier03, Clark09}.  For reproducibility, we record the
number of times the random number generator \citep[Mersenne
  twister;][]{MTwister} has been called for use when restarting the
simulations.

@@

We treat Pop II SF with the same prescription as \citet{Wise09}, which
is a modified version of the \citet{Cen92} method but accounts for the
fact that the molecular clouds are resolved.  The critical overdensity
is the same as the Pop III SF model.  In each star-forming region,
seven percent of the cold gas ($T < 10^3$ K) is removed from the grid
and deposited into the star particle.  Each star particle lives for 20
Myr, the maximum lifetime of an OB star.  These stars generate the
majority of the ionizing radiation and SNe feedback in stellar
clusters, thus we ignore lower mass stars.

@@

The Pop II stars emit 6000 hydrogen ionizing photons per baryon over
their lifetime, and we do not consider singly- and doubly-ionizing
helium photons.  We note that low-metallicity stars generate up to a
factor of four more ionizing photons than a solar metallicity
population \citep{Schaerer03} and might be underestimating the
radiative feedback.  Nonetheless this study provides an excellent
first insight in the transition to Pop II SF, as the metal enrichment
is the key ingredient here.  For SN feedback, these stars generate
$6.8 \times 10^{48}$ erg s$^{-1}$ $\Ms^{-1}$ of energy after living
for 4 Myr, which is injected into spheres with a radius of 10 pc.  If
the resolution of the grid is less than 10/3 pc, we deposit the energy
into a $3^3$ cube surrounding the star particle.

@@

\begin{figure*}
  \epsscale{0.8}
  \plotone{f3}
  \epsscale{1}
  \caption{\label{fig:projections} Density-weighted projections of gas
    density (top), temperature (middle), and metallicity (bottom) at
    $z=7$.  The left column shows the entire simulation volume, where
    the center and right columns focus on the intense and quiet halos.
    The metallicity projections are a composite picture of metals
    originating from Pop III (red) and Pop II (blue) stars with purple
    indicating a mixture of the two.}
\end{figure*}

Here we present the gaseous and stellar evolution of two selected
halos in the simulation: one that has an early mass buildup but no
major mergers after $z=12$, and one that experiences a series of major
mergers between $z=10$ and $z=7$.  We name the halos ``quiet'' and
``intense'', respectively.  We start with the mass accretion history
and enrichment of the halos.  We then compare the nature of the
stellar populations in these halos.

@@

Figure \ref{fig:evo} shows the total, metal-enriched stellar, and gas
mass history of the most massive progenitors of both halos.  The quiet
halo undergoes a series of major mergers at $z > 12$, growing by a
factor of 30 to $2.5 \times 10^7 \Ms$ within 150 Myr.  Afterwards it
only grows by a factor of 3 by $z=7$ mainly through smooth accretion
from the filaments and IGM.  It is the most massive halo in the
simulation between redshifts 13 and 10.  At the same time, the intense
halo has a mass $M = 3 \times 10^6 \Ms$, but it is contained in a
biased region on a comoving scale of 50 kpc with $\sim25$ halos with
$M \sim 10^6 \Ms$.  After $z=10$, these halos hierarchically merge to
form a $10^9 \Ms$ halo at $z=7$ with two major mergers at redshifts 10
and 7.9, seen in the rapid increases in total mass in Figure
\ref{fig:evo}.  The merger history of the two halos are not atypical
as dark matter halos can experience both quiescent and vigorous mass
accretion rates in their buildup.

Both halos start forming Pop II stars when $M = 10^7 \Ms$.  This is
consistent with the filtering mass $M_f$ of high-redshift halos when
it accretes mainly from a pre-heated IGM \citep{gnedin98, gnedin00,
  Wise08_Gal}.  Afterwards these halos can cool efficiently through
\hh~cooling, sustaining constant and sometimes bursty SF.  The latter
characteristics are equated with the definition of a galaxy.  The
quiet halo forms $10^5 \Ms$ of stars by $z=9$.  This initial starburst
photo-evaporates the majority of its molecular clouds, in addition to
heating and ionizing the surrounding IGM out to a radius of 10--15 kpc
at $z=9$.  These respectively reduce the in-situ and external cold gas
supply that could feed future SF.

The gas fractions of both halos are depleted from 0.15 to 0.08 by
outflowing shocks driven by ionization fronts and blastwaves in their
initial starbursts.  The quiet halo never recovers to the cosmic
fraction $\Omega_b/\Omega_M$ for the following reason.  The lack of
major mergers of halos above the filtering mass leads to a small gas
fraction because halos with $M < M_f$ are likely photo-evaporated,
hosting diffuse warm gas reservoirs instead of cold dense cores.
During this quiescent period, the halo mainly accretes warm diffuse
gas from the filaments and IGM.  In contrast, the intense halo grows
from major mergers of halos with $M > M_f$.  The progenitor halos
involved in the major mergers are able to host molecular clouds and
have, in general, higher gas fractions.  Between $z=10$ and $z=8$, the
gas fraction increases from 0.07 to 0.12 until it jumps to 0.14 when a
gas-rich major merger occurs.  The stellar mass accordingly increases
with the ample supply of gas during this period.  The gas fraction
then decreases by 0.01 when galactic outflows are generated from the
starburst associated with this major merger.

@@

The evolution of the stellar and gas metallicity of both halos are
illustrated in Figure \ref{fig:Zevo}.  PISNe from Pop III stars enrich
the nearby IGM out to a radius of 10 kpc and provides a metallicity
floor of $[Z_3/H] \sim -3$, given $M_{\rm char} = 100 \Ms$.  The
metallicity from Pop II SNe initially enrich the ISM of both halos to
an average $[\bar{Z}_2/H]$ between --3.5 and --3.  The quiet halo is
enriched to $[\bar{Z}_2/H] \sim -2.5$ until the metal-poor inflows
balance the metal-rich galactic outflows, which are directed in the
polar directions of the gas disk, keeping the adjacent filaments
metal-poor.  These features and a well-mixed ISM
\citep[cf.][]{Wise08_Gal, Greif10} are apparent in the metallicity
projections in Figure \ref{fig:projections}.  The average stellar
metallicities is equal or slightly higher up to 0.5 dex than
$[\bar{Z}_2/H]$.

In the intense halo, the first few Pop II star clusters have [Z/H]
between --1 and --2 and dominate the average stellar metallicity at $z
> 8$.  Afterwards the metallicity increases itself by a factor of 30
to $[\bar{Z}_2/H] = -1.5$ through self-enrichment from a starburst.
Because this halo is located in a large-scale overdensity, most of the
ejecta falls back into the halo after reaching distances up to 20
comoving kpc, in turn keeping the halo gas metallicity high because
the inflows are relatively metal-rich themselves.  After the $z \sim
8$ starburst, the average stellar metallicity follows the average gas
metallicity within 0.1 dex.

@@

\textit{Quiet halo}.--- The most massive progenitor interestingly
never hosts a Pop III star.  Instead a nearby halo forms a Pop III
star, which (randomly) produces a PISNe at $z=16$.  The blastwave
overruns the most massive progenitor, and the dense core survives this
event and is enriched by this PISN, triggering the transition to Pop
II SF.  Other progenitors host three Pop III stars, forming at $z =
15.4, 14.2, 13.8$, with the latter producing a PISN.  Metal enrichment
from these two PISNe and Pop II SF quench Pop III SF in this halo.

\textit{Intense halo}.--- The progenitors host a total of 56 Pop III
stars with 21 producing PISNe.  The first forms in a $6 \times 10^5
\Ms$ halo at $z=19$.  Pop III stars form on a regular interval in the
halo's progenitors until $z=9$ when most of these halos enter the
metal-rich bubble surrounding the intense halo.  There are two Pop III
stars forming at $z=7.7$ with [Z/H] = --5.7, whose molecular clouds
were enriched by external blastwaves that only partially enriched the
dense regions \citep{Cen08}.  These sites may form Pop III stars if
dust cooling is efficient below \tento{-4} $Z_\odot$.  The most
massive progenitors of the intense halo cease to form Pop III stars at
$z<12$ because of nearby or intrinsic PISNe.

@@

\begin{figure*}
  \plottwo{f4a}{f4b}
  \caption{\label{fig:pops} The scatter plots show the SF history of
    the quiet (left) and intense (right) halos as a function of
    metallicity at $z=7$.  Each circle represents a star cluster,
    whose area is proportional to its mass.  The open circles in the
    upper right represent sizes of $10^3$, $10^4$, and $10^5$ \Ms~star
    clusters.  The dashed lines in the right panel guide the eye to
    two stellar populations that were formed in two satellite halos,
    merging at $z=7.5$.  The upper histogram collects the SF history
    into 25 equal temporal bins.  The right histogram depicts the
    stellar metallicity distribution.}
\end{figure*}

@@

Figure \ref{fig:pops} shows the SF history (SFH) of both halos.  The
metallicity distribution, SF rates, and metallicity evolution and
spread at a given time can all be extracted from these data.

\textit{Quiet halo}.--- A nearby PISNe provides a metallicity floor of
[Z/H] = --2.8 at which metallicity the first Pop II stars form.  The
stellar metallicity evolution exhibits what is expected from an
isolated system with the stellar feedback steadily enriching the ISM,
resulting in a correlation between stellar age and metallicity.  After
$z=10$ the metallicities plateau at [Z/H] = --2.1 for reasons
discussed in \S\ref{sec:halo}.  The SFR peaks at $z=10$ and decreases
as the cold gas reservoir is depleted.  Around $z=7.5$, a 25:1 minor
merger occurs, and the gas inside the satellite halo is compressed,
triggering metal-poor, [Z/H] = --3.2, SF during its nearest approach.
This halo infalls through a filament, where most of metal enrichment
in the quiet halo occurs in bi-polar flows perpendicular to the galaxy
disk and filament.  The filament and thus this satellite halo remains
relatively metal-poor.  Stars with [Z/H] $<$ --3 compose 1.6 percent
of the total stellar mass.

\textit{Intense halo}.--- In contrast with the quiet halo, the intense
halo undergoes a few mergers of halos with an established stellar
population.  This creates a superposition of age-metallicity tracks in
the SFH, seen in the complexity of Figure \ref{fig:pops}.  The first
two Pop II stellar clusters have an unusually high metallicity [Z/H]
$\sim$ --1, which occurs when a PISN blastwave triggers SF in two
neighboring halos.  Most of the early SF occurs around [Z/H] = --2.5.
At $z=9$, the halo's virial temperature reaches \tento{4} K.  This
combined with a 10:1 merger creates a starburst that quickly enriches
the halo to [Z/H] = --1.5 by $z=8$.  The halo continues to enrich
itself with further SF until $z=7$.  The spikes in the scatter plot
correspond to SN triggered SF in nearby molecular clouds
that are enriched up to a factor of 10 with respect to the ISM.
However the mass fraction of these metal-rich, SN triggered clusters
are small compared to the total stellar mass.  The starburst at $z=9$
creates a bimodal metallicity distribution with peaks at [Z/H] = --2.4
and --1.2 with the metal-rich component mainly being created after the
starburst.  Two systems with sizable stellar components merge into the
halo at $z \sim 8$, and their stellar populations are still
discernible in the metallicity-age plot, whose tracks are noted by
dashed lines.  Stars with [Z/H] $<$ --3 compose 1.8 percent of the
total stellar mass.
